Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-10 main.tex
beginning of DI

@@

\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
\newcommand{\compl}[1]{#1^\complement}
\newcommand{\sublist}[1]{\set{#1}}
\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}

@@

\juihsuan{isn't it given by the first four equations? I think that we use the
notation of negation for atoms and formulas. We may also need to precise that each
predicate symbol $p$ has a dual $\dual{p}$.}

@@

@@

\begin{proof}
  That  $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}. 
  \todo{}\lutz{maybe mention also fn 2-5 in arxiv-paper}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

\subsection{The Linear Variants $\FOMLL$ and $\FOMLS$}

>>>>

\newcommand\aiD {\mathsf{ai}}
\newcommand\faD {\forall}
\newcommand\exD {\exists}
\newcommand\tttD {\ttt}
\renewcommand\wD {\mathsf{w}}
\renewcommand\cD {\mathsf{c}}
\renewcommand\acD {\mathsf{ac}}
\newcommand\mfaD {\mathsf{m_\forall}}
\newcommand\mexD {\mathsf{m_\exists}}

\newcommand{\cons}[1]{\{#1\}}
\newcommand{\Scons}[1]{S\cons{#1}}
\newcommand{\conhole}{\cons{~}}
\newcommand{\Sconhole}{S\conhole}

@@

\newcommand{\graphof}[1]{\llbracket#1\rrbracket}
\newcommand{\compl}[1]{#1^\complement}
%\newcommand{\sublist}[1]{\set{#1}}
%\newcommand{\subst}[2]{#1\mathord{\scriptstyle\mapsto} #2}
\newcommand{\sublist}[1]{[#1]}
\newcommand{\subst}[2]{#1/#2}
\newcommand{\ssubst}[2]{\sublist{\subst{#1}{#2}}}

@@

\juihsuan{isn't it given by the first four equations? I think that we use the
notation of negation for atoms and formulas. We may also need to precise that each
predicate symbol $p$ has a dual $\dual{p}$.}\lutz{we either have to say $\dual{\dual a} = a$ or $\dual{\dual p} = p$. I prefer the first.}

@@

For a proof we refer to reader to any standard textbook, e.g.~\cite{TS:00}.

@@

\begin{proof}
  That  $\graphof A$ is a logical cograph follows immediately from the definition and Theorem~\ref{thm:cograph}. 
  \todo{}\lutz{maybe mention also fn 2-5 in Dominic's arxiv-paper}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \begin{center}
    \framebox{%
      $
      \begin{array}{@{}c@{}}
        \dbox{%
          $
          \begin{array}{c}
            \vlinf{\faD}{}{\Scons{\forall x.\ttt}}{\Scons\ttt}
            \qquad
            \vlinf{\aiD}{}{\Scons{a\vlor\cneg a}}{\Scons\ttt}
            \qquad
            \vlinf{\tttD}{}{\Scons{A\vlan\ttt}}{\Scons A}
            \\ \\[-1ex]
            \vlinf{\sw}{}{\Scons{(A\vlan B)\vlor C}}{\Scons{A\vlan (B\vlor C)}}
            \qquad
            \vlinf{\mix}{}{\Scons{A\vlor B}}{\Scons{A\vlan B}}            
            \\ \\[-1ex]
            \vlinf{\exD}{}{\Scons{\exists x.A}}{\Scons{A\ssubst x t}}
            \qquad
            \vlinf{\fequ}{\text{(where $A\fequ B$)}}{\Scons{A}}{\Scons{B}}
          \end{array}
          $
        }
        \\ \\[-1ex]
        \vlinf{\mfaD}{}{\Scons{\forall x.(A\vlor B)}}{\Scons{(\forall x.A)\vlor(\forall x.B)}}
        \qquad
        \vlinf{\mexD}{}{\Scons{\exists x.(A\vlor B)}}{\Scons{(\exists x.A)\vlor(\exists x.B)}}        
        \\ \\[-1ex]
        \vlinf{\me}{}{\Scons{(A\vlor B)\vlan(C\vlor D)}}{\Scons{(A\vlan C)\vlor(B\vlan D)}}
        \\ \\[-1ex]
        \vlinf{\wD}{}{\Scons{A\vlor B}}{\Scons{A}}
        \qquad
        \vlinf{\acD}{}{\Scons{a}}{\Scons{a\vlor a}}
      \end{array}
      $
    }
  \end{center}
  \caption{Deep inference systems $\FOKS$ (all rules) and $\FOMLS$ (rules in the dashed box)}
  \label{fig:KS1}
\end{figure}

Contrary to standard proof formalisms, like sequent calculi or
tableaux, where inference rules decompose the principal formula along
its root connective, can \emph{deep inference rules} be applied like
rewriting rules inside any (positve) formula or sequent
\bfit{context}, which is denoted as $\Sconhole$, and which is a
formula (resp.~sequent) with exactly one occurrence of the \bfit{hole}
$\conhole$ in the position of an atom. Then $\Scons A$ is the result
of replacing the hole $\conhole$ in $\Sconhole$ with $A$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{The Linear Fragments $\FOMLL$ and $\FOMLS$}
